%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To Create PDF:    xelatex cv_13.tex   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\input{structure.tex} % Include the file specifying document layout
\hyphenpenalty=1000

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{George R. Norfolk -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Flat 5, 59 Gordon Road,\\ % Address line 1
\> Ealing, London. W52AL. \\ % Address line 2
{\bf Date of Birth} \> 2$^{nd}$ June 1992 \\ % Date of birth 
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +44(0)7904 999 301 \\ % Mobile phone
{\bf Email} \> \href{mailto:georgenorfolk@hotmail.co.uk}{georgenorfolk@hotmail.co.uk} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}
\small
I am an eager, reliable, and dedicated Platform Engineer with an enthusiasm for DevOps values and an agile culture. I am passionate about maintaining infrastructure as code and security best practice, as well as upskilling with new tools \& langauges, and reaping the benfits in my day to day work. I have a keen interest in the high-level service role of a DevOps or Platform team and how we interact with and support development teams.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Certifications}

\tabbedblock{
\bf{Oct 2019} \> AWS Certified Sysops Administrator Associate - Amazon Web Services\\[5pt]
\>\+
\textit{Result:} \> Pass (834/1000) \\
}

%------------------------------------------------

\tabbedblock{
\bf{2014-2017} \> Bachelor's Degree - \href{https://www.qmul.ac.uk/}{Queen Mary University of London} \\[5pt]
\>BSc. Astrophysics - \textbf{Second Class Honours: Upper Division} \\
\>\+
\textit{ - 3$^{rd}$ year project: Fortran simulation of 3 body problem totalling 500 Billion iterations.}\\
\textit{ - Elected Social Secretary of Queen Mary Games and Video Gaming society.}\\
}


%------------------------------------------------

\tabbedblock{
\bf{2013-2014} \> Foundation Degree - \href{https://www.qmul.ac.uk/}{Queen Mary University of London} \\[5pt]
\>Science and Engineering Foundation Programme - \textbf{First Class Honours} \\

\>\+
\textit{ - Officer Cadet in the British Army University of London Officer Training Corps.}\\
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{May 2019 -}{Present}
{LexisNexis, Lexis House, 30 Farringdon St, London, EC4A 4HH.}
{https://www.lexisnexis.co.uk/}
{DevOps / Cloud Engineer}
{
I joined the London Platform Engineering team in March 2019 with Sparta Global, and after good performance, became a full-time employee of LexisNexis two months later. In the time since joining, I have had the following responsibilties and experience:

\begin{itemize-noindent}[noitemsep]
\setlist{nosep}
\item{Deployment of legacy and modern web apps into AWS using Jenkins, Packer, and Terraform.}
\item{Monitoring and Management of AWS accounts using Jenkins, Python scriping, and Terraform for select AWS services (VPC, IAM, Config, SSM).}
\item{Defined \& documented best practice Jenkins deployments into AWS, used to deploy previously on-premesis sophisticated web application.}
\begin{itemize-noindent}[noitemsep]
\item{Including AWS CLI \& credential best practices, secretsmanager integration, security gates, and basic deployment testing.}
\end{itemize-noindent}
% \item{Deploying dummy application onto Kubernetes cluster, and supporting teams utilising the cluster.}
\item{Executed multiple InfoSec initiatives, including IAM least privilege, Infra as Code, networking, software scanning, security gates, etc.}
\item{Driving force behind my team's agile transformation, advocating within team and enlisting help from outside of team.}
\end{itemize-noindent}

\rule{0mm}{5mm}\textbf{Technologies:} AWS, Jenkins, Packer, Terraform, Python, Docker, Kubernetes.}

%------------------------------------------------

\job
{Nov 2017 -}{April 2019}
{Sparta Global, 6th Floor, 125 London Wall, London, EC2Y 5AS.}
{https://www.spartaglobal.com/}
{Consultant}
{
Prior to employment, I unrdertook 12 weeks of programming training, specialising in DevOps technologies. I attained a placement at LexisNexis ES in Leeds, before transferring to LexisNexis UK in London for the final two months. In this time I gained the following experience:

\begin{itemize-noindent}[noitemsep]
\item{Owner of support for Azure \& on premesis environments, triage of Windows machines and Dynamics 365 application.}
% \item{Developed C\# data transformation process on behalf of the Automation Lead.}
\item{Contributed to my team's agile \& Kanban transformation, and was a member of the company agile Community of Practice.}
\end{itemize-noindent}

\rule{0mm}{5mm}\textbf{Technologies:} Azure Cloud, Azure DevOps, Powershell, C\#, VMWare, Microsoft Dynamics 365, Windows OS.}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Technology}
{
  \textit{\textbf{AWS Cloud}} - Hourly use of varied and core services, backed up by AWS SysOps Associate certification. \\
  \textit{\textbf{Jenkins (Groovy)}} - Defined best practice Jenkins deployment pipelines, utilised across department. \\
  \textit{\textbf{Terraform}} - Deployed Apps and AWS services via Terraform, continuously improved best practice. \\
  \textit{\textbf{Linux OS}} - Daily management of AmazonLinux2 instance fleet via SSH terminal. \\
  \textit{\textbf{Packer}} - Defined best practice integration with Jenkins pipelines, and other best practice for Packer. \\
  \textit{\textbf{Windows OS}} - Support and management of varied Windows environemnts over 4+ years in LN, and more. \\
  \textit{\textbf{Python}} - Authored and deployed suite of Python Lambdas, regular improvement of reporting scripts. \\
  \textit{\textbf{Bash / Unix}} - Constant interaction with Linux machines via SSH, and regular bash scripting. \\
  \textit{\textbf{Kubernetes}} - Took, improved, and delivered internal training course for deploying onto LN cluster. \\
  \textit{\textbf{Docker}} - Authored dockerfiles for deployments onto cluster, taught fundermentals in internal training. \\
  \textit{\textbf{Powershell}} - Debugged, improved, and wrote Windows instance management scripts. \\
  \textit{\textbf{Azure Pipelines}} - Created and delivered course content on core Pipelines concepts including labs. \\
  \textit{\textbf{Ansible}} - Debugged and improved ansible scripts and deployments for legacy applications. \\
  \textit{\textbf{Azure Cloud}} - Supported development environments, with user management and cost analysis. \\
  \textit{\textbf{Splunk}} - Written and updated basic Splunk data calls. \\
  \textit{\textbf{LaTeX}} - This CV is written in LaTeX. \\
}

\skillgroup{Soft Skills}
{  
  \textit{\textbf{Teacher}} - Delivered and improved upon ten-session kuberenetes internal training course. \\
  \textit{\textbf{Mentor}} - Mentored junior team members, helped identify and fill knowledge gaps. \\
  \textit{\textbf{Coach}} - Coached struggling development team in technical skills and ways of working. \\
  \textit{\textbf{Agile Practices}} - Designed and facilitated team Retrospectives and Show \& Tells. \\
  \textit{\textbf{Agile Culture}} - Enthusiast and driver of agile transformation and improvement within team. \\
  \textit{\textbf{DevOps}} - Continued advocation of DevOps practices and culture across department. \\
}

% \skillgroup{Programming Languages / Tools}
% {
% % \textit{Environment} - AWS, Azure, VMWare \\
% % \textit{Tools} - Jenkins, Azure Pipelines, GoCD \\
% % \textit{Languages} - Python, Powershell, C\#, Terraform, Groovy \\
% % \textit{Infra As Code} - Terraform, Groovy, Packer, Kubernetes, Docker \\
% % \textit{OS} - Linux, Windows
% \textit{Strong} - AWS Cloud, Linux OS, Jenkins/Groovy, Terraform, Packer \\
% \textit{Good} - Windows OS, Python, bash, Azure Pipelines \\
% \textit{Basics} - Azure Cloud, Powershell, Kubernetes, Docker, VMWare \\
% \textit{Foundational} - C\#, GoCD, Ansible

% }

%------------------------------------------------

% \skillgroup{Agile}
% {
% \textit{Agile / Kanban transformation within a DevOps team}\\
% \textit{Definition of team mission statement, goals, customers}\\
% \textit{Advocate of DevOps and agile culture \& values}
% }

%------------------------------------------------

% \skillgroup{Personal Project}
% {
% \textit{Application} - Ruby on Rails, HTML, CSS, JavaScript\\
% \textit{Database} - PostgreSQL\\
% \textit{Infrastructure} - AWS, Packer, Terraform v0.12 Infra as Code\\
% \textit{Deployment} - Jenkins in Blue-Green configuration
% }

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{Interests}

% \interestsgroup{
% \interest{Jogging, Badminton, Cycling.}
% \interest{Creative Writing.}
% \interest{Arts and Crafts.}
% \interest{Tabletop, Role Playing, and Video Games.}
% }

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Adrian Farnell \\ % Referee name
{\bf Company} \> Lloyds Banking Group \\ % Referee company
{\bf Position} \> Lead Engineer \\ % Referee job title 
{\bf Email} \> \href{mailto:adrian.farnell@lloydsbanking.com}{adrian.farnell@lloydsbanking.com} \\ % Referee email
{\bf Phone} \> +44(0)7760 172 759 % Referee phone number
\end{tabbing}}
\hfill % Horizontal space between the two blocks
%\parbox{0.5\textwidth}{ % Second block
%\begin{tabbing}
%\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
%{\bf Company} \> Burbank Buy More \\ % Referee company
%{\bf Position} \> Store Manager \\ % Referee job title 
%{\bf Email} \> \href{mailto:mike@buymore.com}{mike@buymore.com} \\ % Referee email
%{\bf Phone} \> +44(0)7904 999 301 % Referee phone number
%\end{tabbing}}

%----------------------------------------------------------------------------------------

\end{document}